---
title: "MSc Data Science & Analytics: LSM Track Data Cleaning & Exploration"
author: "Jill Daly"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: 
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 2
---

<!-- 
Online information about creating technical documents with RMarkdown and knitr:
https://bookdown.org/
https://bookdown.org/yihui/bookdown/
https://rmarkdown.rstudio.com/
https://github.com/rstudio/rmarkdown
https://rmarkdown.rstudio.com/pdf_document_format
http://kbroman.org/knitr_knutshell/pages/Rmarkdown.html
https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf
https://yihui.name/knitr/options/?version=1.2.830&mode=desktop#code-chunk
https://stackoverflow.com/questions/12546365/subfigures-or-subcaptions-with-knitr/49086985#49086985
https://rmarkdown.rstudio.com/articles_report_from_r_script.html
-->

<!-- TODO: Create separate .tex files to deal with styling issues, eg. toc on same page as title -->
\newpage 
\tableofcontents 
\listoffigures
\listoftables
\newpage

<!--##########################################################################
##############################################################################
##                                                                          ##
##                               DATA WRANGLING                             ##
##                       FOR LOADING & TIDYING DATASET                      ##  
##                                                                          ##
##############################################################################
##############################################################################-->


<!--##########################################################################
##                            SCRIPT CONFIG VALUES                          ##
##                                                                          ##
##          These are the hardcoded values that need to be configured       ##
##          for each data capture                                           ##
##############################################################################-->

```{r config, include=FALSE}
# Modules used by this script
source("InstallImport.R")
source("LoadControllerLogs.R")
source("LoadSensorData.R")
source("EDA.R")

# Required Packages
install_imports(c("tidyverse", "VIM", "kableExtra", "PerformanceAnalytics", "Hmisc")) 


# Hardcoded paths used in this script
DATA_PATH <- "../../../data"
DC2_LOGS_PATH <- paste(DATA_PATH, "Data_Capture_2_ControllerLogs", sep = "/")
DC2_ALL_LOGS <- paste(DC2_LOGS_PATH, '.', sep = "/")
DC2_EXCEL <- paste(DATA_PATH, "Data_Capture_2_Raw.xlsx", sep = "/")
```



```{r sensorheader, include=FALSE}
sensor_header = c("IMU1_X",	"IMU1_Y",	"IMU1_Z",	
                  "IMU2_X",	"IMU2_Y",	"IMU2_Z",
                  "IMU3_X",	"IMU3_Y",	"IMU3_Z",
                  "IMU4_X",	"IMU4_Y",	"IMU4_Z",
                  "IMU5_X",	"IMU5_Y",	"IMU5_Z",
                  "IMU6_X",	"IMU6_Y",	"IMU6_Z",
                  "IMU7_X",	"IMU7_Y",	"IMU7_Z",
                  "IMU8_X",	"IMU8_Y",	"IMU8_Z",
                  "IMU9_X",	"IMU9_Y",	"IMU9_Z",	
                  "IMU10_X",	"IMU10_Y",	"IMU10_Z",
                  "IMU11_X",	"IMU11_Y",	"IMU11_Z",	
                  "IMU12_X",	"IMU12_Y",	"IMU12_Z",
                  "Timestamp",	"Delta")

# This header swap is hardcoded specifically for the May Data Capture. 
# This swap is to account for orientation of the sensor.
swap_position_header = c("IMU1_Y",	"IMU1_X",	"IMU1_Z",	
                         "IMU2_X",	"IMU2_Y",	"IMU2_Z", 
                         "IMU3_X",	"IMU3_Y",	"IMU3_Z",
                         "IMU4_X",	"IMU4_Y",	"IMU4_Z",
                         "IMU5_X",	"IMU5_Y",	"IMU5_Z",
                         "IMU6_X",	"IMU6_Y",	"IMU6_Z",
                         "IMU7_Z",	"IMU7_X",	"IMU7_Y",
                         "IMU8_Y",	"IMU8_X",	"IMU8_Z",
                         "IMU9_Z",	"IMU9_X",	"IMU9_Y",	
                         "IMU10_X",	"IMU10_Y",	"IMU10_Z",
                         "IMU11_X",	"IMU11_Y",	"IMU11_Z",	
                         "IMU12_X",	"IMU12_Y",	"IMU12_Z",
                         "Timestamp",	"Delta")

# Axes to negate (using the post converted axis (already adjusted for orientation)
negate_hdr <- c("IMU1_Y", "IMU3_Y", "IMU3_Z", "IMU8_Z", "IMU9_Y", "IMU9_Z", "IMU12_Y", "IMU12_Z")
```




<!--##########################################################################
##                             LOAD CONTROLLER LOGS                         ##
##                                                                          ##
##          Intentionally loading these as separate entities,               ##
##          so that we can analyse the data in isolation,                   ##
##          and find corrlataions                                           ##
##############################################################################-->
\newpage
# Controller Logs  

```{r loadlogs, include=FALSE}
# Create a list of data frames for the controller log files 
controller_logs <- load_controller_logs(DC2_ALL_LOGS)
```



This is a sample controller Log file:
```{r strlogfiles, echo=FALSE}
cl_str <- capture.output(str(controller_logs[[1]]))

# kable Api details: https://rdrr.io/cran/knitr/man/kable.html
# kableExtra ides:
# https://www.r-exercises.com/2018/02/05/how-to-use-kableextra-and-rmarkdown-to-create-tables-in-pdf-documents/

# latex_options of hold_postion and scale_down are very important. 
# Without these, the table is not readable and outside of the flow 
# of the data. See:
# https://stackoverflow.com/questions/49550731/knitr-kable-table-moving-to-the-end-of-page-when-adding-caption-figure-label
# https://stackoverflow.com/questions/49044753/scale-kable-table-to-fit-page-width
knitr::kable(cl_str, 
             caption = "Sample Controller Log File - Structure", 
             format="latex", 
             booktabs=TRUE, 
             row.names = FALSE, 
             col.names = FALSE) %>% 
  kable_styling(latex_options=c("scale_down", "hold_position")) 
```


```{r summlogfiles, echo=FALSE}
cl_summ <- summary(controller_logs[[1]])
knitr::kable(cl_summ, caption = "Controller Log File - Summary", format="latex", booktabs=TRUE) %>% 
  kable_styling(latex_options=c("scale_down", "hold_position"))
```


There is only one log file with missing data, as is demonstrated with the data below. This is because the log file `Acc_1_Vel_4_Test2` has a extra columns included, which have been added after the data capture.  
```{r log_nas, echo=FALSE}
cl_nas <- capture.output(str(map_dfc(controller_logs, function(x) { sum(!complete.cases(x))} )))
knitr::kable(cl_nas, caption = "Controller Missing Data - Summary", format = "latex", booktabs=TRUE)%>% 
  kable_styling(latex_options=c("hold_position"))
```


Here is a summary of contoller log file dimensions for each run:
  ```{r logfiledetails, echo=FALSE}
# Visualise NAs, and get summary of the data here, pre-dropping of NA cols
cl_dets <- map_df(names(controller_logs), sensor_summary, dfl = controller_logs)
knitr::kable(cl_dets, caption = "Controller Datasets")
```

```{r logfilecount, echo=FALSE}
# Get the full, raw observation count
cl_n_count <- sum(cl_dets$r_count)
```

The total observation count for the all controller logs is `r cl_n_count`.

***
  
  <!--##########################################################################
#                     LOAD THE DATA FILE FOR SENSOR DATA                     #
##############################################################################-->


```{r load_sensor_files, echo=FALSE}
# Create a list of data frames for the magnetic and vibration sensor data 
sensor_data <- load_sensor_raw(DC2_EXCEL, sensor_header)
```


```{r loadsensor, include=FALSE}
# Create a list of data frames for the magnetic and vibration sensor data 
# Adjust the XYZ order of axes to account for sensor orientation
# Adjust for gravity calibration 
sensor_data <- convert_axis(sensor_data, swap_position_header, negate_hdr)
```

\newpage
# Sensor (Mag/Acc) Data Files

TODO - Enter notes here about the different type of data


Here are sample plots displaying the amount of missing sensor data from the a sample raw dataset
This is due to some sensors not funtioning during the data capture, due to a number of technical issues.  
The second plot represents the rig where the platform was not present. 

```{r aggrsensorfiles-pre, echo=FALSE}
sensor_aggr(sensor_data[[1]])
sensor_aggr(sensor_data[[20]])
```


```{r, echo=FALSE}
# Drop Columns & Rows with only NAs, as these are empty variables/rows
# due to mechanical issues and should not be included
sensor_data <- drop_na_only_cols(sensor_data, .15)
```

***


```{r sensorfilecount, echo=FALSE}
# Get the full, raw observation count
s_dets <- map_df(names(sensor_data), sensor_summary, dfl = sensor_data)
s_n_count <- sum(s_dets$r_count)
```


```{r separate_sdata}
# Seperate out the magnetic / acc and X / Y / Z sensor data
s_mag_data <- filter_mag_sdata(sensor_data)
s_acc_data <- filter_acc_sdata(sensor_data)

# Create DFs of all X axes data (with accel, vel, plat incluced)
s_mag_x_df <- map_df(s_mag_data, sensor_col_names, col_str = "X|velocity|acceleration|platform")
s_mag_y_df <- map_df(s_mag_data, sensor_col_names, col_str = "Y|velocity|acceleration|platform")
s_mag_z_df <- map_df(s_mag_data, sensor_col_names, col_str = "Z|velocity|acceleration|platform")

s_acc_x_df <- map_df(s_acc_data, sensor_col_names, col_str = "X|velocity|acceleration|platform")
s_acc_y_df <- map_df(s_acc_data, sensor_col_names, col_str = "Y|velocity|acceleration|platform")
s_acc_z_df <- map_df(s_acc_data, sensor_col_names, col_str = "Z|velocity|acceleration|platform")


# Create separate lists with DFs of X axes for a given run
s_mag_x_data_list <- lapply(s_mag_data, extract_axes, axis_str = "X")
s_mag_y_data_list <- lapply(s_mag_data, extract_axes, axis_str = "Y")
s_mag_z_data_list <- lapply(s_mag_data, extract_axes, axis_str = "Z")

s_acc_x_data_list <- lapply(s_acc_data, extract_axes, axis_str = "X")
s_acc_y_data_list <- lapply(s_acc_data, extract_axes, axis_str = "Y")
s_acc_z_data_list <- lapply(s_acc_data, extract_axes, axis_str = "Z")

```


The total observation count for sensor data is `r s_n_count`  
This is a sample sensor data file:
```{r strsdfiles, echo=FALSE}
s_str <- capture.output(str(sensor_data[[1]]))
knitr::kable(s_str, 
             caption = "Sample Sensor Data File - Structure", 
             format="latex", 
             booktabs=TRUE, 
             col.names = "Data Structure") %>% 
  kable_styling(latex_options=c("scale_down", "hold_position"))
```

```{r summsensorfiles, echo=FALSE }
s_summ <- summary(sensor_data[[1]])
knitr::kable(s_summ, caption = "Sample Sensor Data File - Summary") %>% 
  kable_styling(latex_options=c("scale_down", "hold_position"))
```

  
  
This is a summary of the sensor data file dimensions (after dropping columns with 85% or more NAs)
```{r sensorfiledetails, echo=FALSE}
# Get summary of the data here, pre-dropping of NA cols
knitr::kable(s_dets, caption = "Sensor Datasets") %>% 
  kable_styling(latex_options=c("hold_position"))
```


***
  
Here are sample plots displaying the amount of missing sensor data after removing columns with missing
data above the 85% threshold. 

```{r aggrsensorfiles-post, echo=FALSE}
sensor_aggr(sensor_data[[1]])
sensor_aggr(sensor_data[[20]])
```




<!--##########################################################################
#                                   EDA                                      #
##############################################################################-->











<!--  TODO - Show hist plot matrix for the X, Y, Z (Mag; Acc sensors)
TODO - Show box plot matrix for the X, Y, Z (Mag; Acc sensors)
TODO - Show summary of correlation for all sensors
TODO - Show matix correlation for all IMU_X Acc sensors
TODO - Show matix correlation for all IMU_Y Acc sensors
TODO - Show matix correlation for all IMU_Z Acc sensors
TODO - Show matix correlation for all IMU_X Mag sensors
TODO - Show matix correlation for all IMU_Y Mag sensors
TODO - Show matix correlation for all IMU_Z Mag sensors  -->
  
