---
title: "MSc Data Science & Analytics: LSM Track Data Exploration"
author: "Jill Daly"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: 
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 2
---

<!-- 
Online information about creating technical documents with RMarkdown and knitr:
https://bookdown.org/
https://bookdown.org/yihui/bookdown/
https://rmarkdown.rstudio.com/
https://github.com/rstudio/rmarkdown
https://rmarkdown.rstudio.com/pdf_document_format
http://kbroman.org/knitr_knutshell/pages/Rmarkdown.html
https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf
https://yihui.name/knitr/options/?version=1.2.830&mode=desktop#code-chunk
https://stackoverflow.com/questions/12546365/subfigures-or-subcaptions-with-knitr/49086985#49086985
https://rmarkdown.rstudio.com/articles_report_from_r_script.html
-->

<!-- TODO: Create separate .tex files to deal with styling issues, eg. toc on same page as title -->
\newpage 
\tableofcontents 
\listoffigures
\listoftables
\newpage


<!--##########################################################################
##############################################################################
##                                                                          ##
##                               DATA EXPLORATION                           ##
##                         FOR LOADING & TIDYING DATASET                    ##  
##                                                                          ##
##############################################################################
##############################################################################-->


```{r config, include=FALSE}
# Modules used by this script
source("InstallImport.R")
source("SensorDataPreparation.R")
source("EDA.R")

# Required Packages
install_imports(c("tidyverse", "VIM", "kableExtra", "PerformanceAnalytics", "Hmisc", "outliers", "psych")) 
```


<!-- FIGURES FROM SECTIONS CAN BE SAVED TO DISK FOR THE FINAL THESIS DOCUMENT -->


\newpage

```{r sensor_postion, include=FALSE}
# IMU Sensor Positions:
s_pos_df <- data.frame(t(c("IMU1_POS"="FRONT_SURFACE", 
                         "IMU3_POS"="TOP_SURFACE_WITH_PALETTE",
                         "IMU7_POS"="FRONT_SURFACE", 
                         "IMU8_POS"="FRONT_SURFACE", 
                         "IMU9_POS"="SIDE_SURFACE", 
                         "IMU11_POS"="TOP_SURFACE", 
                         "IMU12_POS"="TOP_SURFACE")))
```



## Summary 

```{r create_summary_list, include=FALSE}
summ_list <- lapply(names(sensor_data_list), summarise_sensorlist_by_axis, df_list=sensor_data_list)
```


`r stringr::str_interp("${summ_list[[1]][1]} Sensor Summary")`
```{r echo=FALSE}
# print title 1
k_df <- as.data.frame(summ_list[[1]][2])
knitr::kable(k_df)%>% 
  kable_styling(latex_options=c("hold_position"))
```


`r stringr::str_interp("${summ_list[[1]][1]} Sensor Summary")`
```{r echo=FALSE}
# print title 1
k_df <- as.data.frame(summ_list[[1]][3])
knitr::kable(k_df)%>% 
  kable_styling(latex_options=c("hold_position"))
```

`r stringr::str_interp("${summ_list[[1]][1]} Sensor Summary")`
```{r echo=FALSE}
# print title 1
k_df <- as.data.frame(summ_list[[1]][4])
knitr::kable(k_df)%>% 
  kable_styling(latex_options=c("hold_position"))
```


`r stringr::str_interp("${summ_list[[4]][1]} Sensor Summary")`
```{r echo=FALSE}
# print title 1
k_df <- as.data.frame(summ_list[[4]][2])
knitr::kable(k_df)%>% 
  kable_styling(latex_options=c("hold_position"))
```


# Dataset Details

## FREQUENCY OF CLASS LABEL
```{r class_frequency, include=FALSE}
sen_xtabs <- ftable(xtabs(~ State + Velocity + Acceleration, data = gather_axes))

sen_prop_mar <- prop.table(addmargins(xtabs(~ State + Velocity + Acceleration, data = gather_axes)))

sen_prop <- prop.table(table(gather_axes$State))

```


```{r plot_class_frequency, echo=FALSE}
knitr::kable( sen_xtabs, caption = "XTabs")%>% 
  kable_styling(latex_options=c("scale_down", "hold_position"))

knitr::kable( sen_prop_mar, caption = "prop.table margins")%>% 
  kable_styling(latex_options=c("scale_down", "hold_position"))

knitr::kable( sen_prop, caption = "prop.table")%>% 
  kable_styling(latex_options=c("scale_down", "hold_position"))

```


```{r balance, include=FALSE}
sen_dim <- dim(gather_axes)
sen_smm <- summary(gather_axes)

sen_des_by_state <- describeBy(gather_axes, gather_axes$State)
sen_des <- describe(gather_axes)

sen_hmisc_des <- Hmisc::describe(gather_axes)
```


```{r plot_balance, echo=FALSE}
knitr::kable( as.data.frame(sen_dim, row.names = c("n", "variables")), caption = "Dimensions")%>% 
  kable_styling(latex_options=c("scale_down", "hold_position"))

knitr::kable( as.data.frame(sen_smm), caption = "Sensor Summary")%>% 
  kable_styling(latex_options=c("scale_down", "hold_position"))


```




```{r summary}
install_imports(c("tidyverse", "VIM", "kableExtra", "PerformanceAnalytics", "Hmisc", "outliers", "psych")) 
dim(tidy_sensor_df)
summary(tidy_sensor_df)

describeBy(tidy_sensor_df, tidy_sensor_df$State)
describe(tidy_sensor_df)

Hmisc::describe(tidy_sensor_df)
```

```{r data, include=FALSE}
acc_df <- sensor_data %>% dplyr::filter(Type == "ACC")
mag_df <- sensor_data %>% dplyr::filter(Type == "MAG")

mag_X_df <- mag_df %>% dplyr::select(contains("_X"))
mag_Y_df <- mag_df %>% dplyr::select(contains("_Y"))
mag_Z_df <- mag_df %>% dplyr::select(contains("_Z"))

acc_X_df <- acc_df %>% dplyr::select(contains("_X"))
acc_Y_df <- acc_df %>% dplyr::select(contains("_Y"))
acc_Z_df <- acc_df %>% dplyr::select(contains("_Z"))
```


# UNIVARIATE (DISTRIBUTION, SUMMARY, DESCRIBE)

## Histogram
```{r histograms}
hist(mag_X_df)
hist(mag_Y_df)
hist(mag_Z_df)
hist(acc_X_df)
hist(acc_Y_df)
hist(acc_Z_df)
```


## Boxplots
```{r}
boxplot(mag_X_df, )
boxplot(mag_Y_df)
boxplot(mag_Z_df)
boxplot(acc_X_df)
boxplot(acc_Y_df)
boxplot(acc_Z_df)
```


## CORRELATION
```{r corrplot-mag-x, echo=FALSE}


par(mar=c(6.1,5.1,2.1,1.1), oma=c(0,0,1,0), mfrow=c(1, 2))
plot_object_acc_z <- chart.Correlation(acc_Z_df, histogram=TRUE, pch=19)  
title(paste("Vibration Z Axis Data"), outer = TRUE) # 4 is the mag data
dev.off()

par(mar=c(6.1,5.1,2.1,1.1), oma=c(0,0,1,0), mfrow=c(1, 2))
plot_object_acc_x <- chart.Correlation(acc_X_df, histogram=TRUE, pch=19)  
title(paste("Vibration X Axis Data"), outer = TRUE) # 4 is the mag data
dev.off()

par(mar=c(6.1,5.1,2.1,1.1), oma=c(0,0,1,0), mfrow=c(1, 2))
plot_object_x <- chart.Correlation(mag_X_df, histogram=TRUE, pch=19)  
title(paste("Magnetometer X Axis Data"), outer = TRUE) # 4 is the mag data
dev.off()

par(mar=c(6.1,5.1,2.1,1.1), oma=c(0,0,1,0), mfrow=c(1, 2))
plot_object_y <- chart.Correlation(mag_Y_df, histogram=TRUE, pch=19)  
title(paste("Magnetometer X Axis Data"), outer = TRUE) # 4 is the mag data
dev.off()

par(mar=c(6.1,5.1,2.1,1.1), oma=c(0,0,1,0), mfrow=c(1, 2))
plot_object_z <- chart.Correlation(mag_Z_df, histogram=TRUE, pch=19)  
title(paste("Magnetometer X Axis Data"), outer = TRUE) # 4 is the mag data
dev.off()
```


## OUTLIERS








## ANOVA
```{r}
gathered_df <- mag_X_df %>% 
  gather(key = "X_Sensor", value = "X_Value")

gathered_df %>% group_by(X_Sensor) %>%
  summarise(mean_reading = mean(X_Value, na.rm = TRUE), sd_reading = sd(X_Value, na.rm = TRUE))


gathered_df$X_Sensor <- as.factor(gathered_df$X_Sensor)

head(gathered_df)
levels(gathered_df$X_Sensor)
nlevels(gathered_df$X_Sensor)

bwplot(X_Value~X_Sensor, data = gathered_df, pch="|")

grubbs.test(gathered_df$X_Value[gathered_df$X_Sensor == "IMU1_X"])

model_sensor <- aov(gathered_df$X_Value~gathered_df$X_Sensor)
summary(model_sensor)
summary.lm(model_sensor)

contrasts(gathered_df$X_Sensor)
contrasts(gathered_df$X_Sensor) <- contr.sum
model_sensor <- aov(gathered_df$X_Value~gathered_df$X_Sensor)
summary(model_sensor)
summary.lm(model_sensor)

plot.design(gathered_df$X_Value~gathered_df$X_Sensor)
model.tables(model_sensor)

contrasts(gathered_df$X_Sensor) <- NULL

TukeyHSD(model_sensor)
plot(TukeyHSD(model_sensor))

plot(model_sensor)
```





